### 2021-04-05 Chapter-2/Chapter-2.tex
Updates from Overleaf

Based on the above attacks, some work~\cite{brickell2011technologies} suggests not having secret-dependent memory accesses at coarser than cache line granularity should be secure enough. However, recent studies shows that having memory accesses within a cache line is also dangerous. One example is the CacheBleed attack~\cite{yarom2017cachebleed}. It is a cache channel attack can exploits cache-back collisions.
\subsection{Page-level Channel}
Page channel attacks allow an attacker can observe the memory access at the granularity of memory pages. One example is the controlled-channel attack~\cite{xu2015controlled}, where a privileged adversary try to infer the sensitive information by manipulating the enclave page access. Those kinds of attacks usually happen on the shielding system. A malicious OS can proactively revoke a virtual enclave memory page from the memory. If the victim enclave program accesses the memory table, then the adversary can know which page is accessed by observing the page fault sequences. While the granularity of the controlled-channel attacks is coarse-grained, the controlled-channel attacks allow the attacker to have a noise-free observation. Other examples like the TLB side-channel attack, DDRAM attacks share the same page-level granularity.

In this paper, we consider three types of granularity: byte (1 Byte), cache line size (64 Bytes), page size (4 KBs). To the best of our knowledge, the three types of granularities can cover most of the side-channel attacks in literature.

\subsection{Target Applications}
While there is a vast number of studies\cite{yarom2017cachebleed,191010,184415,Osvik2006,liu2015last} on side-channel attacks, we find many of those work targets on the encryption key on cryptography libraries. In general, current side-channel attacks can be classified into the below three categories.

@@

The first side-channel attack of cryptography libraries can be traced back to Kocher's timing attacks~\cite{kocher1996timing} in 1996. Many algorithms (Diffie-Helloman, RSA) implementations at that time use the simple modular exponentiation algorithm, which does not run in fixed time. By measuring the time differences between the modular exponentiation algorithm computes the exponent bits (0 or 1), Kocher's attack can recover the whole secret key bit by bit. Cryptography libraries usually have several implementations for symmetric ciphers.

>>>>

Based on the above attacks, some work~\cite{brickell2011technologies} suggests not having secret-dependent memory accesses at coarser than cache line granularity should be secure enough. However, recent studies shows that having memory accesses within a cache line is also dangerous. One example is the CacheBleed attack~\cite{yarom2017cachebleed}. It is a cache channel attack can exploits cache-bank collisions.
\subsection{Page-level Channel}
Page channel attacks allow an attacker can observe the memory access at the granularity of memory pages. One example is the controlled-channel attack~\cite{xu2015controlled}. It is a primary threats for the trusted execution environments (TEEs).  A privileged adversary (e.g., Kernel) can infer the sensitive information by manipulating the enclave page access. A malicious OS can proactively revoke a virtual enclave memory page from the memory. If the victim enclave program accesses the memory table, then the OS can observe the page faults and  know which page is accessed. While the granularity of the controlled-channel attacks is coarse-grained, the controlled-channel attacks allow the attacker to have a noise-free observation. Other examples like the TLB side-channel attack, DDRAM attacks share the same page-level granularity.

Based on the above discussion, we consider three types of granularity: byte (1 Byte), cache line size (64 Bytes), page size (4 KBs) in the dissertation. To the best of our knowledge, the three types of granularities can cover most of the side-channel attacks in the literature.

\subsection{Target Applications}
There is a vast number of studies\cite{yarom2017cachebleed,191010,184415,Osvik2006,liu2015last} on side-channel attacks. Most early work targets on the encryption key on cryptography libraries. In recent years, researchers start to focus on more general target applications. In summary, current side-channel target applications can be classified into the below three categories.

@@

The first side-channel attack of cryptography libraries can be traced back to Kocher's timing attacks~\cite{kocher1996timing} in 1996. It exploits the the simple modular exponentiation algorithm function in many algorithms (Diffie-Helloman, RSA) implementations. The function does not run in a fixed time. By measuring the time differences between the modular exponentiation algorithm computes the exponent bits (0 or 1), Kocher's attack can recover the whole secret key bit by bit. Since then, researchers start to break all kinds of cipher implementation through side-channel attacks.   Cryptography libraries usually have several implementations for symmetric ciphers.
